### 2011-11-06 doc/pldi2012/circuit.tex
circuit

Line 17 declares the main simulator function, which accepts a \emph{Circuit}
to be simulated.  In addition to specifying the return type and the types and
names of the formal parameters, it must also specify which regions of memory
it will access, how it will access them (e.g. read-only, read-write, or with
reductions), and what coherence guarantees are needed (e.g. exclusive access).
The regions listed in these access declarations may be anything in the static
scope of the function definition, the formal parameters, or fields of the formal
parameters.  In our example, the simulation of the circuit will need to read
and write all of the nodes and all of the wires in the circuit, and it must
be done with exclusive access to ensure a correct result.

@@

Lines 19-27 are responsible for partitioning the circuit into \emph{MAX\_PIECES}
pieces that can be worked on in parallel.  In order to partition a region, we
need to provide a \emph{coloring}, which is a relation over the valid elements
in a region and a set of ``colors''.  Our current implementation uses small
integers or booleans for the names of colors, but any enumerable set would be
fine.  The coloring relation need not be total - it can leave out some elements entirely.  And although it is not required to be injective (it can map a single
element to multiple colors), the fact that injective mappings will always
result in disjoint subregions makes them strongly encouraged (when possible).

Our example uses four colorings to help create the partitions of the circuit.
A graph partitioning algorithm
(not shown) is run on to divide the nodes of the graph into \emph{MAX\_PIECES}
subsets.  (These subsets are hopefully reasonably compact, but the correctness
of the simulation is not dependent on that.)  The thick lines in \ref{sfig:part_fig:pvs}
show a how the nodes in a small graph might be partitioned into 3 subsets.
Once the subsets are known, the \emph{node\_owner\_map} is created by assigning
each node a color corresponding to which subset it was placed in.  The 
\emph{wire\_owner\_map} assigns each wire to the same subset as its ``in\_node''.
The \emph{node\_nghbr\_map} maps a node to color(s) of all wires that 
connect to it.  Finally, the \emph{node\_sharing\_map} is derived from the
\emph{node\_nghbr\_map}, with a node colored ``true'' if any colors other than 
its own were used, and ``false'' if the only wires that connect to a node are
in the same piece.
Figure~\ref{fig:part_fig} shows how the partitions are defined.

Line 19 uses the \emph{wire\_owner\_map} to partition the wires region of the
circuit into a subregion for each piece, but the partitioning of the nodes is
more complicated due to the sharing that is necessary between the pieces.
First, the \emph{node\_sharing\_map} is used to create two subregions: $p\_nodes\_pvs[false]$ contains all the nodes that are private to some piece (i.e. will
never be needed for the computations in any other piece), while $p\_nodes\_pvs[true]$ contains nodes that will be accessed by multiple pieces' computations.
Each of these subregions is then partitioned using the $node\_owner\_map$ to
create the subregions owned by each computation.  These are the $p_i$ and $s_i$
subregions, shown in figures \ref{sfig:part_fig:p_i} and \ref{sfig:part_fig:s_i}.  Finally, the $g_i$ subregions (shown in figure~\ref{sfig:part_fig:g_i}) are
created using the $node\_nghbr\_map$ to 
create subregions that include the ``ghost'' nodes needed to perform each
piece's calculations.

@@

Lines 34-38 form the bulk of the actual simulation, performing three passes
over the circuit on each iteration.  For each pass, a for loop is used to 
spawn a task for each piece of the circuit.  There are no explicit requests for
parallel execution, nor is there explicit synchronization required between the
passes.  As we will see, bBoth the fact that the pieces can be run in parallel
for a single 
pass and the the required inter-task dependencies are determined automatically
by the runtime based on the region access annotations on the task declarations.

>>>>

Line 17 declares the main simulator function, which takes a
\emph{Circuit} to be simulated.  This function specifies the regions it
will access as well as the {\em permissions} and {\em coherence}
properties it requires of those regions.  In this case, the {\tt RWE}
annotation specifies that the function accesses {\tt c.r\_all\_nodes}
and {\tt c.r\_all\_wires} with read-write permissions and exclusive
access (the strongest coherence mode).  The simulation of the circuit
will read and write all of the nodes and all of the wires, and it must
be done with exclusive access to ensure a correct result.  Functions that
declare their accessed regions, permissions, and coherence properties are
called {\em tasks} and will be considered by the Legion runtime for parallel
execution.

@@

Lines 19-27 are responsible for partitioning the circuit into \emph{MAX\_PIECES}
pieces that can be worked on in parallel.  In order to partition a region, we
need to provide a \emph{coloring}, which is a relation over the valid elements
in a region and a set of colors.  
%Our current implementation uses small
%integers or booleans for the names of colors, but any enumerable set would be
%fine.  The coloring relation need not be total - it can leave out some elements entirely.  And although it is not required to be injective (it can map a single
%element to multiple colors), the fact that injective mappings will always
%result in disjoint subregions makes them strongly encouraged (when possible).
Our example uses four colorings to  create circuit partitions.
A graph partitioning algorithm
(not shown) divides nodes of the graph into \emph{MAX\_PIECES}
subsets.  
%(These subsets are hopefully reasonably compact, but the correctness
%of the simulation is not dependent on that.)  
The thick lines in \ref{sfig:part_fig:pvs}
show how the nodes in a small graph might be partitioned into 3 subsets.
Once the subsets are known, the \emph{node\_owner\_map} is created by assigning
each node the color corresponding to its subset.  The 
\emph{wire\_owner\_map} assigns each wire to the same subset as its ``in\_node''.
The \emph{node\_nghbr\_map} maps a node to color(s) of all wires that 
connect to it.  Finally, the \emph{node\_sharing\_map} is derived from the
\emph{node\_nghbr\_map}, with a node colored ``true'' if any colors other than 
its own were used, and ``false'' if the only wires that connect to a node are
in the same piece.
Figure~\ref{fig:part_fig} shows how the partitions are defined.

Line 19 uses the \emph{wire\_owner\_map} to partition the wires region of the
circuit into a subregion for each piece, but the partitioning of the nodes is
more complicated due to the sharing that is necessary between the pieces.
First, the \emph{node\_sharing\_map} is used to create two subregions: $p\_nodes\_pvs[false]$ contains all the nodes that are private to some piece (i.e. will
never be needed for the computations in any other piece), while $p\_nodes\_pvs[true]$ contains nodes that will be accessed by multiple pieces' computations.
Each of these subregions is then partitioned using the $node\_owner\_map$ to
create the subregions owned by each computation.  These are the $p_i$ and $s_i$
subregions, shown in Figures \ref{sfig:part_fig:p_i} and \ref{sfig:part_fig:s_i}.  Finally, the $g_i$ subregions (shown in Figure~\ref{sfig:part_fig:g_i}) are
created using the $node\_nghbr\_map$ to 
create subregions that include the ``ghost'' nodes needed to perform each
piece's calculations.

@@

Lines 34-38 form the bulk of the actual simulation, performing three passes
over the circuit on each iteration.  For each pass, a for loop is used to 
spawn a task for each piece of the circuit.  There are no explicit requests for
parallel execution, nor is there explicit synchronization required between the
passes.  As we will see, both the fact that the pieces can be run in parallel
for a single 
pass and the the required inter-task dependencies are determined automatically
by the runtime based on the region access annotations on the task declarations.
